https://gerrit.wikimedia.org/r/Documentation/rest-api-changes.html#suggest-reviewers - API to suggest reviewers based on a prefix - need to look into the method is uses to recommend someone. Used on the gerrit interface when you search for a user. Likely based on simple metrics due to it being a prefix search.



Todo this week:
* Requirements
* Introduction
* Good amount of work on Related work

* Data collected in the majority or what is to be initially collected
* Test data

For the next meeting there will be something to look at for the writing


In two weeks:
* Very simple recommender implemented for last meeting before easter
* By last meeting before easter getting 

3 meetings after easter
* First looking and catchup

* First four by end of easter holidays
* Agents done by end easter


Order of priority:
* Agents
* Write about agents
* Evaluation
* Write about evaluation
* Maybe: Optional goals if time




For Monday:
* First four sections touch up ready for reviewer
* Template for the poster

For Tuesday:
* Presentation ready enough for a practice
* Some good progress on evaluation
* Compare simple and neural network

Add poster at end of presentation so I can present it briefly

Flow diagram from data collection to implementation

Briefly comment about optional goals in the conclusion as future work.

Optional goal about modifying results can say rule-based kind of did this if you modified the weights.

For Wedesdany 10th ready for review:
* Conckusuin
* Evlaution
* Abstract

Brief for the manuals in this document - Versions for things I've used.




Order of priority:
* Evaluation
* Diagram
* Table for data set numbers
* Poster and presentation
* Psuedo-code
* Conclusion
* Abstract

Evaluation, conclusion and abstract done by Thursday morning.

Graph of evaluation scores to repo size.

Maybe add data I collected to evaluation by evaluating - low priority.

Psuedo code in time for review.

Detail why changes were not working on the university 